Embedded Meta-Learning: Toward more flexible deep-learning models

### 2019-07-29 writing/nips_submission/response/EML_response.tex
Revised with some comments from Jay

\textbf{The insight of our paper is that meta-mappings over polynomials are exactly analogous to basic meta-learning of a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of input polynomials and output polynomials for a more abstract function that operates over polynomials (e.g. multiplying by 2). These polynomials are embedded as above, by passing examples of them through the meta network to compute a function embedding. We then can take these pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for this meta-task. Just as above, we can pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2. We can then pass a probe polynomial through $F$ to produce a predicted output. The only differences from the basic case are 1) where the inputs and targets come from and 2) how the loss or evaluation is computed from the predictions. For basic training, we used an appropriate loss in the output space for each task, in meta training, we used an $\ell^2$ between the predicted task embedding, and the embedding of the target task. To evaluate the real performance on a meta-mapping, we actually computed the performance of the predicted output embedding at regressing the target polynomial. For example, if the meta-mapping was ``multiply by 2'' and the probe input was $x + 2$, we would evaluate how closely the predicted output polynomial matched $2x + 4$ by feeding the predicted function embedding to the hyper network to parameterize a function, feeding inputs to this function, and then measuring its predicted outputs. We hope this clarifies how our architecture works, and why it is fundamentally different from prior work. All three reviewers highlighted the novelty of considering transformations over tasks. That is the conceptual contribution of our paper, but the architectural contribution of our paper is to show a way that meta-mappings can be parsimoniously integrated into a meta-learning architecture without adding a single parameter. We show in Appendix D.1 that this actually performs better than having separate meta and hyper networks for basic tasks and meta-mappings. These conceptual and architectural contributions are the main points of the paper, natural language and continual learning are side points, so we are revising the main text to clarify this. \par 

>>>>

\textbf{The insight of our paper is that meta-mappings over polynomials are exactly analogous to basic meta-learning of a polynomial.} Instead of having examples of inputs and outputs for a single polynomial, we have examples of input polynomials and output polynomials for a more abstract function that operates over polynomials (e.g. multiplying by 2). These polynomials are embedded as above, by passing examples of them through the meta network to compute a function embedding. We then can take these pairs of (embedded input polynomial, embedded target polynomial), and pass them through the \textbf{exact same meta network} $\mathcal{M}$ to produce an embedding for this meta-task. Just as above, we can pass this function embedding through the same hyper network $\mathcal{H}$ to parameterize a function $F$ which attempts to multiply polynomials by 2. We can then pass a probe polynomial through $F$ to produce a predicted output. The only differences from the basic case are 1) where the inputs and targets come from and 2) how the loss or evaluation is computed from the predictions. For basic training, we used an appropriate loss in the output space for each task, in meta training, we used an $\ell^2$ between the predicted task embedding, and the embedding of the target task. To evaluate the real performance on a meta-mapping, we actually computed the performance of the predicted output embedding at regressing the target polynomial. For example, if the meta-mapping was ``multiply by 2'' and the probe input was $x + 2$, we would evaluate how closely the predicted output polynomial matched $2x + 4$ by feeding the predicted function embedding to the hyper network to parameterize a function, feeding inputs to this function, and then measuring its predicted outputs. We hope this clarifies how our architecture works, and why it is fundamentally different from prior work. All three reviewers highlighted the novelty of considering transformations over tasks. That is the conceptual contribution of our paper, but the architectural contribution of our paper is to show a way that meta-mappings can be parsimoniously integrated into a meta-learning architecture without adding a single parameter. We show in Appendix D.1 that this actually performs better than having separate meta and hyper networks for basic tasks and meta-mappings. These conceptual and architectural contributions are the main points of the paper, natural language and continual learning are side points. (We are revising the main text to clarify this.) \par 
